Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
rewrite intro

% Our method
\newcommand{\our}{DNN2SGP\xspace}

@@

%Current state of affairs 
Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}. These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

%Need for adaptive learning methods + failures with current methods
In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}. In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows for the consolidation of contributions from {\em all} training data into a sparse representation. Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs. Through the dual parameter formulation, we establish a connection between the neural network, the resulting full GP, and a sparse approximation similar to variational sparse GPs~\cite{titsias2009variational}. Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}. Thus we are able to avoid retraining and condition new data in to our model. The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.
%\todo{a pragraph on how this can be used for improving CL and RL}

@@

\begin{figure}[t!]
  \centering\scriptsize
  % Figure options
  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
  % Set figure 
  \setlength{\figurewidth}{.28\textwidth}
  \setlength{\figureheight}{\figurewidth}
  %
  \def\inducing{\normalsize Sparse inducing points}
  %
  \begin{subfigure}[c]{.34\textwidth}
    \raggedleft
    \pgfplotsset{ylabel={Output, $y$}}
    \input{./fig/regression-nn.tex}%
  \end{subfigure}
  \hfill  
  \begin{subfigure}[c]{.01\textwidth}
    \centering
    \tikz[overlay,remember picture]\node(p0){};
  \end{subfigure}  
  \hfill
  \begin{subfigure}[c]{.28\textwidth}
    \raggedleft
    \pgfplotsset{yticklabels={,,},ytick={\empty}}
    \input{./fig/regression-nn2svgp.tex}%
  \end{subfigure}
  \hfill  
  \begin{subfigure}[c]{.01\textwidth}
    \centering
    \tikz[overlay,remember picture]\node(p1){};
  \end{subfigure}  
  \hfill
  \begin{subfigure}[c]{.28\textwidth}
    \raggedleft
    \pgfplotsset{yticklabels={,,},ytick={\empty}}        
    \input{./fig/regression-update.tex}%
  \end{subfigure}
  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network. Center:~Our approach summarizes the...}
  \label{fig:teaser} 
  % 
  \begin{tikzpicture}[remember picture,overlay]
    % Arrow style
    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
    % Arrows
    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
    \node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
    % Arrow labels
    \node[font=\scriptsize\sc,color=white] at (p0-arr) {nn2svgp};
    \node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};   
  \end{tikzpicture}
\end{figure}

@@

    % Arrow labels
    \node[font=\scriptsize\sc,color=white] at (first-arr) {nn2svgp};
    \node[font=\scriptsize\sc,color=white] at (second-arr) {\normalsize$\bm\approx$};

@@

  \end{tikzpicture}
  \newcommand{\mycircle}{\protect\tikz[baseline=-.5ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
  \newcommand{\mysquare}{\protect\tikz[baseline=-.5ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
  %
  \caption{Binary classification (\mysquare~vs.~\mycircle) on the {\sc banana} toy data data set. We convert the left-hand neural network  }
  \label{fig:banana}  
\end{figure}

\section{Background}
\label{sec:methods}

In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising
its weights.
% a GP posterior -- can be obtained
% around the Maximum a Posteriori (MAP) weights.

@@

In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
%
\begin{equation} \label{eq-empirical-risk}
  \weights^{*} = 
  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{equation}
%
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

\textbf{Linearization gives rise to a Gaussian process}
Our goal is to build a sparse function-space representation of a neural network.
Gaussian processes are an extension of the multivariate normal that characterizes a distribution over
functions in terms of the first two moments.
They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
lead to function space equivalent approximations.
As Gaussian distributions remain tractable under linear transformations, a linear function in
terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i).
\end{equation}
% The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
with the Generalized Gaussian-Newton approximation (GGN).
Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}_i) = \Jac{\weights_*}{\mathbf{x}_i} \, \weights$, where $\Jac{\weights}{\mathbf{x}_i} \coloneqq \nabla_\weights f(\mathbf{x}_i)^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
Therefore, the GGN approximate linear model can be used to convert our weight space model to the function space by,
\begin{equation} 
\label{eq-laplace-approx-function-space}
% g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
  \mu(\vx) =  0 \quad \text{and} \quad
  \kappa(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\JacT{\weights^*}{\mathbf{x}'},
\end{equation}
where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}). With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$. \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.\todo{The reader may wonder what is pseudo-data then A: Is this better?} Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model. Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$. In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments. We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation. \todo{this sentence can be avoided probably, A: its what Aidan calls setting the scene}

\section{Methods}
\paragraph{Linearization in the dual parameters}
As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
\begin{equation}  \label{eq:gp_pred}
 \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
\mathrm{Var}_{p(f_{i}\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
where $f_i = f_\weights(\vx_i)$, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
\end{equation}\todo{ More explination of the dual equation 6 the loss landscape link. Perbutation point linked directly to that here. }
%
The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. The above relations holds for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. The question is how do we form the dual variables without access to the exact posterior and different approximate inference techniques solve the question in different ways. Bound techniques such as \citet{jaakkola1997variational} attempt to bound the integral thus making the integral tractable, while Expecation Propogation (EP) as used in \citet{csato2002sparse} iteratively finds dual variables but sets them to log of the expectation of the approximate posterior. Meanwhile variational inference  \cite{khan2017conjugate, adam2021dual} find them using the variational approximation of the posterior to solve the integral.

@@

\subsection{Continual Learning}
% Definition of CL -> a sequence of tasks

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/uci.tex}
\end{table}

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/img_super.tex}
\end{table}
\subsection{Updating the representation during continual learning}

>>>>

% Our method
\newcommand{\our}{\textsc{dnn2sgp}\xspace}

@@

%Current state of affairs 
Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}. These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

%Need for adaptive learning methods + failures with current methods
In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}. In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows for the consolidation of contributions from {\em all} training data into a sparse representation. Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs. Through the dual parameter formulation, we establish a connection between the neural network, the resulting full GP, and a sparse approximation similar to variational sparse GPs~\cite{titsias2009variational}. Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}. Thus we are able to avoid retraining and condition new data in to our model. The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.

@@

\begin{figure}[t!]
  \centering\scriptsize
  % Figure options
  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
  % Set figure 
  \setlength{\figurewidth}{.28\textwidth}
  \setlength{\figureheight}{\figurewidth}
  %
  \def\inducing{\large Sparse inducing points}
  %
  \begin{subfigure}[c]{.34\textwidth}
    \raggedleft
    \pgfplotsset{ylabel={Output, $y$}}
    \input{./fig/regression-nn.tex}%
  \end{subfigure}
  \hfill  
  \begin{subfigure}[c]{.01\textwidth}
    \centering
    \tikz[overlay,remember picture]\node(p0){};
  \end{subfigure}  
  \hfill
  \begin{subfigure}[c]{.28\textwidth}
    \raggedleft
    \pgfplotsset{yticklabels={,,},ytick={\empty}}
    \input{./fig/regression-nn2svgp.tex}%
  \end{subfigure}
  \hfill  
  \begin{subfigure}[c]{.01\textwidth}
    \centering
    \tikz[overlay,remember picture]\node(p1){};
  \end{subfigure}  
  \hfill
  \begin{subfigure}[c]{.28\textwidth}
    \raggedleft
    \pgfplotsset{yticklabels={,,},ytick={\empty}}        
    \input{./fig/regression-update.tex}%
  \end{subfigure}
  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network. Middle:~Our approach summarizes all the training data with the help of an iducing set of points. The model captures the predictive mean and uncertainty, and (right) makes it possible to update the model with new data without degrading previous performance.}
  \label{fig:teaser} 
  % 
  \begin{tikzpicture}[remember picture,overlay]
    % Arrow style
    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
    % Arrows
    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
    \node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
    % Arrow labels
    \node[font=\scriptsize\sc,color=white] at (p0-arr) {\our};
    \node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};   
  \end{tikzpicture}
\end{figure}

@@

    % Arrow labels
    \node[font=\scriptsize\sc,color=white] at (first-arr) {\our};
    \node[font=\scriptsize\sc,color=white] at (second-arr) {\normalsize$\bm\approx$};

@@

  \end{tikzpicture}
  \newcommand{\mycircle}{\protect\tikz[baseline=-.6ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
  \newcommand{\mysquare}{\protect\tikz[baseline=-.6ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
  \newcommand{\myinducing}{\protect\tikz[baseline=-.7ex]\protect\node[circle,inner sep=1.5pt,draw=black,fill=black]{};}
  %
  \caption{\textbf{Uncertainty quantification} for binary classification (\mysquare~vs.~\mycircle). We convert the trained neural network (left) to a sparse GP model that summarizes all data onto a sparse set of inducing points~\myinducing\ (middle). This gives similar behaviour as would running full Hamiltonian Monte Carlo (HMC) on the original neural network model weights (right). Marginal uncertainty depicted by colour intensity.\looseness-1}
  \label{fig:banana}  
\end{figure}

\section{Background: Function-space representation of neural networks}
\label{sec:methods}
%
%In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising its weights.
% a GP posterior -- can be obtained
% around the Maximum a Posteriori (MAP) weights.

@@

In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
%
\begin{equation} \label{eq-empirical-risk}
  \weights^{*} = 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{equation}
%
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

\textbf{Linearization gives rise to a Gaussian process}
Our goal is to build a sparse function-space representation of a neural network.
Gaussian processes are an extension of the multivariate normal that characterizes a distribution over
functions in terms of the first two moments.
They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
lead to function space equivalent approximations.
As Gaussian distributions remain tractable under linear transformations, a linear function in
terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i).
\end{equation}
% The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
with the Generalized Gaussian-Newton approximation (GGN).
Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}_i) = \Jac{\weights_*}{\mathbf{x}_i} \, \weights$, where $\Jac{\weights}{\mathbf{x}_i} \coloneqq \nabla_\weights f(\mathbf{x}_i)^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
Therefore, the GGN approximate linear model can be used to convert our weight space model to the function space by,
\begin{equation} 
\label{eq-laplace-approx-function-space}
% g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
  \mu(\vx_i) =  0 \quad \text{and} \quad
  \kappa(\mathbf{x}_i, \mathbf{x}_i')
  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}_i}\JacT{\weights^*}{\mathbf{x}_i'},
\end{equation}
where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}). With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$. \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.\todo{The reader may wonder what is pseudo-data then A: Is this better?} Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model. Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$. In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments. We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation. \todo{this sentence can be avoided probably, A: its what Aidan calls setting the scene}

\section{\our: Sparse function-space represenation of neural networks}
\paragraph{Linearization in the dual parameters}
As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
\begin{equation}  \label{eq:gp_pred}
 \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
\end{equation}\todo{ More explination of the dual equation 6 the loss landscape link. Perbutation point linked directly to that here. }
%
The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. The above relations holds for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. The question is how do we form the dual variables without access to the exact posterior and different approximate inference techniques solve the question in different ways. Bound techniques such as \citet{jaakkola1997variational} attempt to bound the integral thus making the integral tractable, while Expecation Propogation (EP) as used in \citet{csato2002sparse} iteratively finds dual variables but sets them to log of the expectation of the approximate posterior. Meanwhile variational inference  \cite{khan2017conjugate, adam2021dual} find them using the variational approximation of the posterior to solve the integral.

@@

\subsection{Sparse functional regularization (SFR) in continual learning}
% Definition of CL -> a sequence of tasks

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/uci.tex}
\end{table}
We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets. The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$. After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification. Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}. We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds. During the initial NN training, we used a learning rate of $1e-3$.

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/img_super.tex}
\end{table}

Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks. After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}. We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

In addition to uncertainty estimates, our method can update the posterior when given new data. We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE]. 
\subsection{Updating the representation during continual learning}
